\LARGE \bf Preparation of Papers for IEEE Sponsored Conferences \& Symposia*

### 2017-04-08 bmc.tex
.

    \figref{vdp-map} shows the cells and the trajectory segments which
    are part of the data sets constructed using the $1$-relational
    modeling. Against each cell, its unique identifier (integer
    co-ordinate) is mentioned.  Finally, \figref{vdp-graph} and
    \tabref{vdp-pwa} show the enriched graph $G^R$ with its transition
    relations. Note that self loops result when an observed trajectory
    segment has its $start$ and $end$ states in the same cell.

@@

\inclfig[width=0.95\linewidth]{vdp_cont_traces.pdf}{Van der
Pol: continuous trajectories. Red and green boxes indicate unsafe and
initial sets.}
\label{fig:vdp-cont}

\inclfig[width=0.95\linewidth]{vdp_abs.pdf}{The discovered
abstraction $\scr{H}(0.1)$. Red cells are unsafe cells and green cells are
initial cells.}
\label{fig:vdp-abs}

\inclfig[width=0.90\linewidth]{vdp_disc_map.pdf}{Cells and
trajectory segments used by $1$-relational modeling.}
\label{fig:vdp-map}

\inclfig[width=0.50\linewidth]{vdp_graph.pdf}{Enriched
graph $G^R$. The affine maps $f$ for the transition relations are show
in \tabref{vdp-pwa}.}
\label{fig:vdp-graph}

>>>>

    \figref{vdp-map} shows the cells and the trajectory segments, which
    are part of the data sets constructed using the $1$-relational
    modeling. Against each cell, its unique identifier (integer
    co-ordinate) is mentioned.  Finally, \figref{vdp-graph} and
    \tabref{vdp-pwa} show the enriched graph $G^R$ with its transition
    relations. Note that self loops result when an observed trajectory
    segment has its $start$ and $end$ states in the same cell.

@@

\inclfig[width=0.95\linewidth]{vdp_cont_traces.pdf}{Van der
Pol: continuous trajectories. Red and green boxes indicate unsafe and
initial sets.}{vdp-cont}

\inclfig[width=0.95\linewidth]{vdp_abs.pdf}{The discovered
abstraction $\scr{H}(0.1)$. Red cells are unsafe cells and green cells are
initial cells.}{vdp-abs}

\inclfig[width=0.90\linewidth]{vdp_disc_map.pdf}{Cells and
trajectory segments used by $1$-relational modeling.}{vdp-map}

\inclfig[width=0.50\linewidth]{vdp_graph.pdf}{Enriched
graph $G^R$. The affine maps $f$ for the transition relations are show
in \tabref{vdp-pwa}.}{vdp-graph}
